Language-Based Security for Low-Level MPC

### 2024-07-17 ppdp24/bruteforce.tex
checkpoint

We immediately note that $\runs(\prog)$ can be obtained by a left-folding
of $\solvealg$ across $\prog$. 
\begin{lemma}
  \label{lemma-cruns}
  Given $\prog$ where $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$. Define:
  \begin{eqnarray*}
    {tt}\ \ \stores\ (\xassign{x}{\be}{\cid}) &\defeq& \begin{array}{l}
      \mathrm{let}\ \stores' = \solve{\stores}{\be}{\cid}\ \mathrm{in}\\
      \ \ \{\extend{\store}{x}{1} \mid \store \in \stores' \}\ \cup\\
      \ \ \{\extend{\store}{x}{0} \mid \store \in \stores - \stores' \}\end{array}%\\[2mm]
    %\cruns(\prog) &\defeq& \mathit{foldl}\ {tt}\ \mems(S \cup R)\ \prog
  \end{eqnarray*}
  Then assuming default preprocessing, $\mathit{foldl}\ {tt}\ \mems(S \cup R)\ \prog = \runs(\prog)$.
\end{lemma}
However, this method does not take advantage of parallellization,
in that elements of $\runs(\prog)$ can be calculated independently.

@@

  \vars\ (\be_1 \exor \be_2)\ \cid \defeq (\vars\ \be_1\ \cid) \cup (\vars\ \be_2\ \cid)
\end{mathpar}
... and so on. Then, to convert a protocol $\prot$ to a Datalog
we first define the function $\bodies$ that applies $\solvealg$ locally to each command
in $\prog$, obtaining the subset of memories that result
in a variable assignment of $1$.  
\begin{definition} Define:
$$
\bodies(\xassign{x}{\be}{\cid}) \defeq (x, (\solve{(\mems(\vars\ \be\ \cid))}{\be}{\cid}))
$$
\end{definition}
The mapping of $\bodies$ across a program
$\prog$-- i.e., $(\mathit{map}\ \bodies\ \prog)$--  essentially defines the
logic program, modulo some syntactic conversion. We can
accomplish the latter as follows, where $\datalog(\prog)$ defines the
full conversion.
\begin{definition} We define the conversion from memories to
  literals and clause bodies as follows:
\begin{mathpar}
  \logit{x \mapsto 1} \defeq x

>>>>

We immediately note that $\runs(\prog)$ can be obtained by a left-folding
of $\solvealg$ across $\prog$. 
\begin{lemma}
  \label{lemma-cruns}
  Given $\prog$ where $\iov(\prog) = S \cup V \cup O$ and $\flips(\prog) = R$. Define:
  \begin{eqnarray*}
    {tt}\ \ \stores\ (\xassign{x}{\be}{\cid}) &\defeq& \begin{array}{l}
      \mathrm{let}\ \stores' = \solve{\stores}{\be}{\cid}\ \mathrm{in}\\
      \ \ \{\extend{\store}{x}{1} \mid \store \in \stores' \}\ \cup\\
      \ \ \{\extend{\store}{x}{0} \mid \store \in \stores - \stores' \}\end{array}%\\[2mm]
    %\cruns(\prog) &\defeq& \mathit{foldl}\ {tt}\ \mems(S \cup R)\ \prog
  \end{eqnarray*}
  Then assuming default preprocessing, $\mathit{foldl}\ {tt}\ \mems(S \cup R)\ \prog = \runs(\prog)$.
\end{lemma}
However, this method does not take advantage of parallelization,
in that elements of $\runs(\prog)$ can be calculated independently.

@@

  \vars\ (\be_1 \exor \be_2)\ \cid \defeq (\vars\ \be_1\ \cid) \cup (\vars\ \be_2\ \cid)
\end{mathpar}
... and so on. Then, to convert a protocol $\prog$ to a Datalog
we first define the function $\bodies$ that applies $\solvealg$ locally to each command
in $\prog$, obtaining the subset of memories that result
in a variable assignment of $1$.  
\begin{definition} Define:
$$
\bodies(\xassign{x}{\be}{\cid}) \defeq (x, (\solve{(\mems(\vars\ \be\ \cid))}{\be}{\cid}))
$$
\end{definition}
The mapping of $\bodies$ across a program
$\prog$-- i.e., $(\mathit{map}\ \bodies\ \prog)$--  essentially defines the
logic program, modulo some syntactic conversion. We can
accomplish the latter as follows, where $\datalog(\prog)$ defines the
full conversion.
\begin{definition} We define the conversion from memories to
  literals and clause bodies as follows:
\begin{mathpar}
  \logit{x \mapsto 1} \defeq x
